A Gentle Introduction into Structural Causal Models

### 2021-05-02 intro.Rmd
intro

Beyond the school of thought, there is also a hierarchy of causation which Pearl introduced in 2009.
This hierarchy

@@

>>>>

Beyond the school of thought, there is also a hierarchy of causation which Pearl introduced in 2009.

@@

This hierarchy examines different queries, their actions and the respective hierachical rank.
The first query is prediction where we examine based on observations.
The second query is interventions, where we can use Pearls (2009) do-calculus to examine what happens if certain conditions holds.
Note that there are various different types of intervention, such as atomic intervention, where we set a variable to a constant, or e.g. policy intervention where we specify a different function for this specific variable.

```{tikz,fig.cap="Policy Intervention",  fig.align= "center", echo =F}
\usetikzlibrary{calc}
\usetikzlibrary{positioning}
\usetikzlibrary{arrows}
  \begin{tikzpicture}[
    sharp corners=2pt,
    inner sep=6pt,
    node distance=2cm,
    >=latex]
\tikzstyle{my node}=[draw, shape = circle, minimum height=1cm,minimum width=1cm]
\tikzstyle{latent}=[draw, shape = rectangle, minimum height=1cm,minimum width=1cm]
\node[my node, fill=gray!30] (A){A};
\node[latent,left of=A](UA){$U_A$};
\node[my node, fill=gray!70] at ($(A)!0.5!(A)-(0pt,1.5cm)$) (T) {$T_\pi$};
\node[my node,right = 1 cm of T, fill=gray!30](C){C};
\node[latent,left = 1cm of T](UT){$U_T$};
\node[latent,right = 1cm of A](UC){$U_C$};
\draw[->] (A) -- (T);
\draw[->] (UA) -- (A);
\draw[->] (UT) -- (T);
\draw[->] (UC) -- (C);
\draw[->] (A) -- (C);
\draw[->] (T) -- (C);
\end{tikzpicture}
```
